Verifying Demonstrations

### 2018-02-20 paper/ZKPK.tex

>>>>

The Schnorr protocol in itself only provides honest-verifier zero-knowledge.
To achieve malicious-verifier zero-knowledge, we have to choose \(k\) (size of 
the challenge, see \cref{PKalgorithms}) logarithmic in the security parameter 
\(\lambda\) and repeat the protocol sufficiently many times (also logarithmic in 
the security parameter).
